---
title: "Summit Pathology Volumes 2015-2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r libraries, include=FALSE}
library(tidyverse)
library(lubridate)
library(here)
```

```{r import-data, include=FALSE}
# Import raw data --------------------------------------------------------
# All cases from 2015-01-01 - 2022-03-27 ---------------------------------
raw_counts <-
  readr::read_delim(
    here("data", "cases-2015.01.01-2022.03.27.csv"),
    delim = ",",
    col_types = cols(
      Accession = col_double(),
      `Result ID` = col_character(),
      `Client ID` = col_character(),
      `Client Name` = col_character(),
      `Patient Name` = col_character(),
      `Patient ID` = col_character(),
      `Date of Birth` = col_datetime(),
      `Result Created Time` = col_datetime(),
      `Report Released Time` = col_datetime(),
      GUID = col_character(),
      `CPT Code` = col_character(),
      Quantity = col_double(),
      `CPT Created Time` = col_datetime()
    ),
    na = "NULL"
  )
```

```{r summarize-data, include=FALSE}
# Count unique accessions
accessions <- 
raw_counts %>%
  filter(`Result Created Time` < "2022-01-01 00:00:01" & 
           `Report Released Time` < "2022-01-01 00:00:01") %>% 
  mutate(yr = year(floor_date(`Report Released Time`, unit = "year"))) %>%
  group_by(yr) %>% 
  summarise(n_accessions = n_distinct(Accession))

# Count unique Result IDs
result_id <- 
  raw_counts %>%
  filter(`Result Created Time` < "2022-01-01 00:00:01" & 
           `Report Released Time` < "2022-01-01 00:00:01") %>% 
  mutate(yr = year(floor_date(`Report Released Time`, unit = "year"))) %>%
  group_by(yr) %>% 
  summarise(n_result_ids = n_distinct(`Result ID`))

# Count total CPT codes released excluding 80000 (no charge)
cpt_codes <- 
  raw_counts %>%
  filter(`Result Created Time` < "2022-01-01 00:00:01" & 
           `Report Released Time` < "2022-01-01 00:00:01" & 
           `CPT Code` != "80000") %>% 
  mutate(yr = year(floor_date(`Report Released Time`, unit = "year"))) %>%
  group_by(yr) %>% 
  summarise(n_cpt = sum(Quantity, na.rm = TRUE))

# Combine accession, result ID, and CPT counts
volumes <-
  tibble(accessions$yr,
         accessions$n_accessions,
         result_id$n_result_ids,
         cpt_codes$n_cpt) %>%
  rename(
    Year = "accessions$yr",
    Accessions = "accessions$n_accessions",
    `Result IDs` = "result_id$n_result_ids",
    `CPT Codes` = "cpt_codes$n_cpt"
  ) %>% 
  mutate(Year = as.character(Year))
```

## Data included in analysis

All cases signed out between 01-01-2015 and 12-31-2021 were exported from LigoLab and included in the analysis. There were `r  raw_counts %>% summarize(n()) %>% prettyNum(big.mark = ",", scientific = FALSE)` total cases signed out, including cases re-released with revisions. Annual volumes were calculated as the total number of unique accessions, unique Result IDs, and the total count of CPT codes. The 80000 (non-billable) CPT code was excluded from the annual CPT code volume calculations. Table 1 below summarizes volumes by these three metrics from 2015 -- 2021.

```{r summary-table, include=TRUE}
knitr::kable(volumes, format.args = list(big.mark = ",",
  scientific = FALSE), caption = "**Table1. Annual Volumes by Accessions, Result IDs, and CPT Codes**")

gt::gt(volumes)
```

